Structuring College Access: The Market Segment Model and College Board Geomarkets

### 2025-05-14 text/back_end_KS.qmd
LA revisions

Due to the large number of Geomarkets in urban Southern California, we distinguish Los Angeles -- 11 Geomarkets, results shown here -- from Orange County (four Geomarkets) and San Diego (three Geomarkets), which are shown in the Online Appendix. The 11 Geomarkets within the Los Angeles metropolitan area are illustrated in @fig-la-maps by total population across the three census periods. The Los Angeles metropolitan area is one of the only multi-nuclei models in the country that is formed when urban growth occurs around multiple centers that serve different functions rather than expanding from a single central business district core (CITE- Harris and Ullman 1945). As depicted in @fig-la-maps, Geomarkets closely follow this overall metropolitan model. Hollywood and Wilshire, South and South Central Los Angeles, and East Los Angeles Geomarkets are centrally located in the metropolitan area followed by an outer core ring of made up by the Glendale and Pasadena, San Fernando Valley-East, West Los Angeles and West Beach, South Bay, and Long Beach Geomarkets. The San Fernando Valley-West Geomarket is located in the northwest part of the region, whereas Covina and West Covina as well as the Riverside, San Bernadino, and Ontario Geomarkets are located inland, comprising the Inland Empire.

The population growth in the Los Angeles metropolitan area increased from approximately 8 Million in 1980 to more than 12 Million in 2020. @fig-dallas-maps showcases population growth by Geomarkets over the three census periods reflect the urban sprawl forming the multi-nuclei model. The most pronounced increases occurred in South and South Central Los Angeles Geomarket, as well as the outer/inland Geomarkets of San Fernando Valley-West, Riverside and San Bernadino, and Ontario. The South and South Central Los Angeles Geomarket grew from approximately 1.2 to 1.6 Million from 1980 to 2020. In contrast, the San Fernando Valley-West and Riverside and San Bernadino, and Ontario Geomarkets grew from approximately 700,000 to 1.2 Million and from 1.1 Million to nearly 3 Million during this time, respectively.

\@fig-la-rq1-race presents the racial and ethnic composition of each Geomarket within the Los Angeles metropolitan area from 1980 to 2020. Over this period, the proportion of White residents declined across all Geomarkets, while Asian and Hispanic populations generally increased. \[THE CAVEAT THAT WE DON'T HAVE ASIAN FOR 1980 IS MORE IMPORTANT FOR LA\] In 1980, all Geomarkets - except for East Los Angeles, South and South Central Los Angeles, and Hollywood and Wilshire- were predominantly White, with percentages ranging from 62% White in Long Beach to 78% in the San Fernando Valleys (West and East) Geomarkets. By 2020, however, only the West Los Angeles and West Beach Geomarket remained predominantly White (62%). Remanining Geomarkets exhibited a more racially/ethnic diverse population by 2020, including San Fernando Valley-West- (44% White, 4% Black, 39% Hispanic; 11% Asian Pacific Islander), San Fernando Valley -East (43% White, 4% Black, 41% Hispanic; 8% Asian Pacific Islander), Glendale and Pasadena (35% White, 3% Black, 37% Hispanic; 21% Asian Pacific Islander), South Bay (29% White, 12% Black, 33% Hispanic; 21% Asian Pacific Islander), Long Beach (26% White, 11% Black, 46% Hispanic; 13% Asian Pacific Islander), Covina and West Covina (19% White, 3% Black, 52% Hispanic; 24% Asian Pacific Islander), and Riverside, San Bernardino, and Ontario (28% White, 7% Black, 54% Hispanic; 6% Asian Pacific Islander). However, the South and South Central Los Angeles and Hollywood and Wilshire Geomarkets experienced substantial declines in the share of Black residents from 1980 to 2020, dropping from 44% to 18% and 18% to 9%, respectively.

\[I THINK THE LEADS ARE THAT SOUTH CENTRAL (ESPECIALLY), EAST LA, AND WILSHIRE ARE THE POOREST. START TEHRE AND THEN GET TO OTHER RESULTS.\] @fig-la-rq1-ses presents trends in socioeconomic indicators for the Los Angeles metropolitan area from 1980 to 2020. While median income increased across all of the metropolitan area over the three census periods, some shifts occurred in the relative socioeconomic levels across Geomarkets. Many Geomarkets kept their relative levels of affluence from 1980 to 2020. For instance, the Covina and West Covina, South Bay, and San Fernando Valley remained among the most affluent, whereas the San Fernando Valley East, Glendale and Pasadena, Long Beach, and Riverside, San Bernardino, and Ontario Geomarkets remained at middle ranges of affluence and the Hollywood and Wilshire, South and South Central Los Angeles, and East Los Angeles Geomarkets remained at the lowest levels of affluence across the metropolitan area during this period. The West Los Angeles and West Beach Geomarket demonstrated the most substantial increase in median household income, rising from \$112,000 in 1980 to \$132,000 in 2000, and reaching \$137,000 by 2020. This sustained growth positioned it as the most affluent Geomarket in the Los Angeles metropolitan area.

@fig-la-rq1-ses also illustrates shifting levels of poverty across Geomarkets in the Los Angeles metropolitan area over time. In 1980, poverty rates were relatively low (less than 12%) for all Geomarkets except for East Los Angeles (17%), South and South Central Los Angeles (24%), and Hollywood and Wilshire (18%). However, poverty rates declined in South and South Central Los Angeles (22%), remained stable in East Los Angeles and Hollywood and Wilshire, and increased in all other Geomarkets. Such shifts and West of Dallas/Ft. Worth Metroplex, while increasing for all other Geomarkets. These divergent trends resulted in more staggered poverty rates across the metropolitan area by 2020. This includes four Geomarkets with poverty rates less than 10% (San Fernando Valley- West, West Los Angeles and West Beach, South Bay, and Covina and West Covina), four Geomarkets with poverty rates ranging from 11%-15% (San Fernando Valley- East, Glendale and Pasadena, Long Beach, and Riverside, San Bernardino, and Ontario), and three Geomarkets with poverty rates ranging from 16%-22% (Hollywood and Wilshire, East Los Angeles, South and South Central Los Angeles).

Lastly, @fig-la-rq1-ses shows a widening disparity in educational attainment across the Los Angeles metropolitan area. Although all Geomarkets experienced increases in the percentage of residents with a bachelor's degree or higher between 1980 and 2020, the West Los Angeles and West Beach Geomarket experienced a substantially greater increase - from 35% in 1980 to 66% in 2020- widening the gap with other Geomarkets in terms of educational attainment.

\[THINK YOU CAN CUT THIS PARAGRAPH\] The Los Angeles metropolitan area exemplifies a complex multi-nuclei urban model, characterized by decentralized population growth and increasing demographic diversity across its 11 Geomarkets. From 1980 to 2020, the region’s population expanded significantly leading to overall declines in the White population and increases in Hispanic and Asian populations across Geomarkets. West Los Angeles and West Beach is the only majority White Geomarket in 2020. Socioeconomic indicators reveal enduring disparities, especially in historically lower-income Geomarkets like South and South Central Los Angeles, East Los Angeles, and Hollywood and Wilshire. Meanwhile, Geomarkets such as West Los Angeles and West Beach became increasingly affluent and highly educated, highlighting growing socioeconomic and educational divides. Given these demographic shifts within the context of a multi-nuclei urban model, the Los Angeles metropolitan area presents a distinctive Geomarket landscape case in which racial/ethnic enclaves across a range of various socioeconomic levels are distributed across multiple Geomarkets rather than concentrated in one or two.

@@

To examine how the socioeconomic and racial composition of included versus excluded prospects varies when student list purchases filter on particular Geomarkets in the Los Angeles metropolitan areas, we analyze six orders placed by a research university that filtered for prospects across the entire state of California, in the 2019-2020 \[NOT JUST 2019-20. REVISE\] high school graduating class, and by PSAT scores. Two orders indicated PSAT score thresholds ranging from 1070-1180, another two orders filtered for a 1190-1260 PSAT range, and the remaining two orders filtered for scores ranging from 1270-1520.

@fig-la-rq2-race presents the racial/ethnic composition of purchased student profiles. The more than 15,000 prospects in the resulting student lists at the low PSAT score thresholds (1070-1180) reflect very similar racial/ethnic compositions within Geomarkets than overall demographic makeup of the metropolitan area in 2020 (see @fig-la-rq1-race). \[THE LEDE IS SOUTH CENTRAL AND EAST LA. START THERE!\]. However, the racial/ethnic composition of prospects become less proportional to overall metropolitan patterns by Geomarket as PSAT scores increase. For instance, prospect pools at middle range PSAT scores (1190-1260) within Geomarkets become disproportionately more Asian, while the representation of Hispanic and Black prospects decline substantially. This pattern becomes most pronounced at the highest PSAT score prospect pools. \[I DON'T THINK THAT BLACK AND LATINX STUDENTS HAVING LOW TEST SCORES IS THE STORY WE ARE TRYING TO TELL. THAT STORY HAS BEEN TOLD. THE MORE IMPORTANT THING IS, WITHIN SOME TEST THRESHOLD, HOW DOES THE RACIAL COMPOSITION VARY ACROSS GEOMARKETS. LIKE EVEN WITHIN THE MID RANGE, SOUTH CENTRAL, EAST LA, AND INLAND EMPIRE STAND OUT\] <!-- This disproportionate over representation for Asian prospects in comparison to the population of residents with Geomarkets ranges from 3 percentage points in the West Los Angeles and West Beach Geomarket (16% prospects versus 13% Asian residents) to 52 percentage points in the East Los Angeles Geomarket (79% prospects versus 27% residents). @fig-la-rq2-race illustrates the share of Black prospects within these high PSAT orders declines to less than 3% within all Geomarkets in comparison to Black residents making up a range of 3% (Covina and West Covina) to 18% (South and South Central Los Angeles) of residents within Geomarkets. Similar underrepresentation patterns are evident for Hispanic porspects are evident across all Geomarkets execept for a nearly equal representation in South and South Central Los Angeles (73% prospects versus 71% Hispanic residents). -->

@fig-la-rq2-midSAT-race presents the race/ethnicity of all prospects targeted in the middle PSAT score range across Geomarket contributions for the Los Angeles metropolitan area. For the more than 2,500 White prospects in this pool, we see the San Fernando Valley - West (28% versus 20% for all prospects) and the West Los Angeles and West Beach (12% versus 7% for all prospects)Geomarkets contributing disproportionately larger shares.

\[I THINK CLEANER IF YOU JUST HAVE A SMALL PARAGRAPH FOR HISPANIC AND A SMALL PARAGRAPH FOR BLACK. I THINK ONE LEDE ACROSS THESE RESULTS IS RIVERSIDE AS AN ENGINE FOR BLACK/LATINX AND FOR FIRST-GEN STUDENTS. I GET THAT THESE TWO POINTS CONTRADICT EACH OTHER\]. Representational patterns across Geomarkets are reversed for Black and Hispanic prospects in @fig-la-rq2-midSAT-race. South and South Central Los Angeles and Riverside, San Bernadino, and Ontario Geomarkets contributed larger proportions of Black and Hispanic prospects relative to their contributions to the overall prospect pool in the Los Angeles metropolitan area. On the other hand, the San Fernando Valley- West and the Glendale and Pasadena Geomarket contributed smaller proportions of Black and Hispanic Prospects. However, the West Los Angeles and West Beach (10% versus 7% for all prospects), Hollywood Wilshire (7% versus 5% for all prospects), and the Long Beach (8% versus 5% for all prospects) Geomarkets contributed a larger share of Black prospects, whereas Covina and West Covina contributed a larger share of Hispanic students. All other Geomarkets contributed nearly equal shares of Black and Hispanic prospects.

\[I MOVED ASIAN\] For Asian students, the Glendale and Pasadena (17% versus 14% for all prospects), East Los Angeles (11% versus 5% for all prospects) and Covina and West Covina (17% versus 11% for all prospects) Geomarkets contributed a disproportionate larger shares, whereas nearly all other Geomarkets contributed disproportionately smaller or nearly equal shares.

>>>>

Due to the large number of Geomarkets in urban Southern California, we distinguish Los Angeles -- 11 Geomarkets, results shown here -- from Orange County (four Geomarkets) and San Diego (three Geomarkets), which are shown in the Online Appendix. The 11 Geomarkets within the Los Angeles metropolitan area are illustrated in @fig-la-maps by total population across the three census periods. The Los Angeles metropolitan area is one of the only multi-nuclei models in the country that is formed when urban growth occurs around multiple centers that serve different functions rather than expanding from a single central business district core (CITE- Harris and Ullman 1945). As depicted in @fig-la-maps, Geomarkets closely follow this overall metropolitan model. Hollywood and Wilshire, South and South Central Los Angeles, and East Los Angeles Geomarkets are centrally located in the metropolitan area followed by an outer core ring made up by the Glendale and Pasadena, San Fernando Valley-East, West Los Angeles and West Beach, South Bay, and Long Beach Geomarkets. The San Fernando Valley-West Geomarket is located in the northwest part of the region, whereas Covina and West Covina as well as the Riverside, San Bernadino, and Ontario Geomarkets are located inland, comprising the Inland Empire.

The population growth in the Los Angeles metropolitan area increased from approximately 8 Million in 1980 to more than 12 Million in 2020. @fig-la-maps showcases population growth by Geomarkets over the three census periods reflect the urban sprawl forming the multi-nuclei model. The most pronounced increases occurred in South and South Central Los Angeles Geomarket, as well as the outer/inland Geomarkets of San Fernando Valley-West, Riverside and San Bernadino, and Ontario. The South and South Central Los Angeles Geomarket grew from approximately 1.2 to 1.6 Million from 1980 to 2020. In contrast, the San Fernando Valley-West and Riverside and San Bernadino, and Ontario Geomarkets grew from approximately 700,000 to 1.2 Million and from 1.1 Million to nearly 3 Million during this time, respectively.

@fig-la-rq1-race presents the racial and ethnic composition of each Geomarket within the Los Angeles metropolitan area from 1980 to 2020. Over this period, the proportion of White residents declined across all Geomarkets, while Asian and Hispanic populations generally increased. \[THE CAVEAT THAT WE DON'T HAVE ASIAN FOR 1980 IS MORE IMPORTANT FOR LA\] In 1980, all Geomarkets - except for East Los Angeles, South and South Central Los Angeles, and Hollywood and Wilshire- were predominantly White, with percentages ranging from 62% White in Long Beach to 78% in the San Fernando Valleys (West and East) Geomarkets. By 2020, however, only the West Los Angeles and West Beach Geomarket remained predominantly White (62%). Remanining Geomarkets exhibited a more racially/ethnic diverse population by 2020, including San Fernando Valley-West- (44% White, 4% Black, 39% Hispanic; 11% Asian Pacific Islander), San Fernando Valley -East (43% White, 4% Black, 41% Hispanic; 8% Asian Pacific Islander), Glendale and Pasadena (35% White, 3% Black, 37% Hispanic; 21% Asian Pacific Islander), South Bay (29% White, 12% Black, 33% Hispanic; 21% Asian Pacific Islander), Long Beach (26% White, 11% Black, 46% Hispanic; 13% Asian Pacific Islander), Covina and West Covina (19% White, 3% Black, 52% Hispanic; 24% Asian Pacific Islander), and Riverside, San Bernardino, and Ontario (28% White, 7% Black, 54% Hispanic; 6% Asian Pacific Islander). However, the South and South Central Los Angeles and Hollywood and Wilshire Geomarkets experienced substantial declines in the share of Black residents from 1980 to 2020, dropping from 44% to 18% and 18% to 9%, respectively.

<!--# [I THINK THE LEADS ARE THAT SOUTH CENTRAL (ESPECIALLY), EAST LA, AND WILSHIRE ARE THE POOREST. START TEHRE AND THEN GET TO OTHER RESULTS.] --> @fig-la-rq1-ses presents trends in income, poverty, and educational attainment in the Los Angeles metropolitan area from 1980 to 2020, demonstrating the South and South Central Los Angeles, East Los Angeles, and Hollywood and Wilshire Geomarkets remained at the lowest socioeconomic levels across these indicators. For instance, the median household income in the South and South Central Los Angeles Geomarket increased modestly from \$57,000 in 1980 to \$59,000 in 2000, reaching \$67,000 by 2020. In comparison, East Los Angeles and Hollywood and Wilshire recorded slightly higher median incomes in 2020 at \$76,000 and \$84,000, respectively. These figures remain substantially lower than that of the most affluent Geomarket, West Los Angeles and West Beach, where the median household income reached \$137,000 in 2020.

@fig-la-rq1-ses also illustrates parallel trends in poverty and educational attainment over time, with Hollywood and Wilshire, East Los Angeles, South and South Central Los Angeles Geomarkets consistenly ranking at lower levels across these socioeconomic indicators. Moreover, the disparities between these three Geomarkets and all others in the Los Angeles metropolitan area widened from 1980 to 2020.

<!--# In 1980, poverty rates were relatively low (less than 12%) for all Geomarkets except for East Los Angeles (17%), South and South Central Los Angeles (24%), and Hollywood and Wilshire (18%). However, poverty rates declined in South and South Central Los Angeles (22%), remained stable in East Los Angeles and Hollywood and Wilshire, and increased in all other Geomarkets. Such shifts and West of Dallas/Ft. Worth Metroplex, while increasing for all other Geomarkets. These divergent trends resulted in more staggered poverty rates across the metropolitan area by 2020. This includes four Geomarkets with poverty rates less than 10% (San Fernando Valley- West, West Los Angeles and West Beach, South Bay, and Covina and West Covina), four Geomarkets with poverty rates ranging from 11%-15% (San Fernando Valley- East, Glendale and Pasadena, Long Beach, and Riverside, San Bernardino, and Ontario), and three Geomarkets with poverty rates ranging from 16%-22% (Hollywood and Wilshire, East Los Angeles, South and South Central Los Angeles). -->

<!--# Lastly, @fig-la-rq1-ses shows a widening disparity in educational attainment across the Los Angeles metropolitan area. Although all Geomarkets experienced increases in the percentage of residents with a bachelor's degree or higher between 1980 and 2020, the West Los Angeles and West Beach Geomarket experienced a substantially greater increase - from 35% in 1980 to 66% in 2020- widening the gap with other Geomarkets in terms of educational attainment. -->

<!--#  [THINK YOU CAN CUT THIS PARAGRAPH] The Los Angeles metropolitan area exemplifies a complex multi-nuclei urban model, characterized by decentralized population growth and increasing demographic diversity across its 11 Geomarkets. From 1980 to 2020, the region’s population expanded significantly leading to overall declines in the White population and increases in Hispanic and Asian populations across Geomarkets. West Los Angeles and West Beach is the only majority White Geomarket in 2020. Socioeconomic indicators reveal enduring disparities, especially in historically lower-income Geomarkets like South and South Central Los Angeles, East Los Angeles, and Hollywood and Wilshire. Meanwhile, Geomarkets such as West Los Angeles and West Beach became increasingly affluent and highly educated, highlighting growing socioeconomic and educational divides. Given these demographic shifts within the context of a multi-nuclei urban model, the Los Angeles metropolitan area presents a distinctive Geomarket landscape case in which racial/ethnic enclaves across a range of various socioeconomic levels are distributed across multiple Geomarkets rather than concentrated in one or two.-->

@@

To examine how the socioeconomic and racial composition of included versus excluded prospects varies when student list purchases filter on particular Geomarkets in the Los Angeles metropolitan areas, we analyze six orders placed by a research university that filtered for prospects across the entire state of California, in the 2020-2022 high school graduating classes, and by PSAT scores. Two orders indicated PSAT score thresholds ranging from 1070-1180, another two orders filtered for a 1190-1260 PSAT range, and the remaining two orders filtered for scores ranging from 1270-1520.

@fig-la-rq2-race presents the racial/ethnic composition of purchased student profiles. For the more than 15,000 prospects in the resulting student lists at the low PSAT score thresholds (1070-1180), South and South Central Los Angeles (n=1,031) and East Los Angeles (n=871) Geomarket pools stand out as having an overwhelming majority of students of color, 98% and 95% respectively. Relative to other Geomarkets in the Los Angeles metropolitan area, such patterns are attributed to both South and South Central Los Angeles (89%) and East Los Angeles (64%) having substantially greater proportions of Hispanic prosepcts, as well as a larger proportion of Black prospects for South and South Central Los Angeles (6%) and larger share of Asian prospects for East Los Angeles (30%).

Even among higher PSAT score ranges, South and South Central Los Angeles remains the most prominent Geomarket with significant proportions of Hispanic and Black student prospects, while East Los Angeles stands out for its substantial share of Asian prospects.

<!--#  very similar racial/ethnic compositions within Geomarkets than overall demographic makeup of the metropolitan area in 2020 (see @fig-la-rq1-race). [THE LEDE IS SOUTH CENTRAL AND EAST LA. START THERE!]. However, the racial/ethnic composition of prospects become less proportional to overall metropolitan patterns by Geomarket as PSAT scores increase. For instance, prospect pools at middle range PSAT scores (1190-1260) within Geomarkets become disproportionately more Asian, while the representation of Hispanic and Black prospects decline substantially. This pattern becomes most pronounced at the highest PSAT score prospect pools. [I DON'T THINK THAT BLACK AND LATINX STUDENTS HAVING LOW TEST SCORES IS THE STORY WE ARE TRYING TO TELL. THAT STORY HAS BEEN TOLD. THE MORE IMPORTANT THING IS, WITHIN SOME TEST THRESHOLD, HOW DOES THE RACIAL COMPOSITION VARY ACROSS GEOMARKETS. LIKE EVEN WITHIN THE MID RANGE, SOUTH CENTRAL, EAST LA, AND INLAND EMPIRE STAND OUT] <!-- This disproportionate over representation for Asian prospects in comparison to the population of residents with Geomarkets ranges from 3 percentage points in the West Los Angeles and West Beach Geomarket (16% prospects versus 13% Asian residents) to 52 percentage points in the East Los Angeles Geomarket (79% prospects versus 27% residents). @fig-la-rq2-race illustrates the share of Black prospects within these high PSAT orders declines to less than 3% within all Geomarkets in comparison to Black residents making up a range of 3% (Covina and West Covina) to 18% (South and South Central Los Angeles) of residents within Geomarkets. Similar underrepresentation patterns are evident for Hispanic porspects are evident across all Geomarkets execept for a nearly equal representation in South and South Central Los Angeles (73% prospects versus 71% Hispanic residents). -->

@fig-la-rq2-midSAT-race presents the race/ethnicity of all prospects targeted in the middle PSAT score range across Geomarket contributions for the Los Angeles metropolitan area, demonstrating South and South Central Los Angeles (7% versus 2% for all prospects) and Riverside, San Bernadino, and Ontario (25% versus 17% for all prospects) Geomarkets contributed larger proportions of Black prospects relative to their contributions to the overall prospect pool in the Los Angeles metropolitan area. <!--#  For the more than 2,500 White prospects in this pool, we see the San Fernando Valley - West (28% versus 20% for all prospects) and the West Los Angeles and West Beach (12% versus 7% for all prospects)Geomarkets contributing disproportionately larger shares.-->

For Hispanic prospects, South and South Central Los Angeles (8% versus 2% for all prospects) and Riverside, San Bernadino, and Ontario (24% versus 17% for all prospects) also contributed a disproportinately larger proportions of prospects relative to their contributions to the overall pool in the Los Angeles metropolitan area.

<!--# [I THINK CLEANER IF YOU JUST HAVE A SMALL PARAGRAPH FOR HISPANIC AND A SMALL PARAGRAPH FOR BLACK. I THINK ONE LEDE ACROSS THESE RESULTS IS RIVERSIDE AS AN ENGINE FOR BLACK/LATINX AND FOR FIRST-GEN STUDENTS. I GET THAT THESE TWO POINTS CONTRADICT EACH OTHER]. Representational patterns across Geomarkets are reversed for Black and Hispanic prospects in @fig-la-rq2-midSAT-race. South and South Central Los Angeles and Riverside, San Bernadino, and Ontario Geomarkets contributed larger proportions of Black and Hispanic prospects relative to their contributions to the overall prospect pool in the Los Angeles metropolitan area. On the other hand, the San Fernando Valley- West and the Glendale and Pasadena Geomarket contributed smaller proportions of Black and Hispanic Prospects. However, the West Los Angeles and West Beach (10% versus 7% for all prospects), Hollywood Wilshire (7% versus 5% for all prospects), and the Long Beach (8% versus 5% for all prospects) Geomarkets contributed a larger share of Black prospects, whereas Covina and West Covina contributed a larger share of Hispanic students. All other Geomarkets contributed nearly equal shares of Black and Hispanic prospects. -->

For Asian students, the Glendale and Pasadena (17% versus 14% for all prospects), East Los Angeles (11% versus 5% for all prospects) and Covina and West Covina (17% versus 11% for all prospects) Geomarkets contributed a disproportionate larger shares, whereas nearly all other Geomarkets contributed disproportionately smaller or nearly equal shares.

These contribution patterns by race/ethnicity demonstrate that student list orders targeting prospects in the Los Angeles metropolitan area using Geomarket filters that exclude lower-income Geomarkets such as South and South Central Los Angeles and Riverside, San Bernadino, and Ontario Geomarkets would result in the loss of substantially disproportionate shares of Black and Hispanic students from the resulting prospect pools. Similarly, using a Geomarket filter excluding East Los Angeles would result in the loss of disproportionate shares of Asian students.
